# Introduction {.unnumbered}

```{r setup, include=FALSE}
library(palmerpenguins)
library(tidyverse)
library(knitr)
library(patchwork)
```

## Overview of Research Problem

```{r overview-plot, fig.cap="Overview of Study Population Distribution", echo=FALSE}
# Create overview visualization
p1 <- ggplot(penguins, aes(x = species, fill = island)) +
  geom_bar(position = "stack") +
  labs(title = "Population Distribution",
       x = "Species", y = "Count") +
  theme_minimal()

p2 <- ggplot(penguins, aes(x = species, fill = sex)) +
  geom_bar(position = "dodge") +
  labs(title = "Sex Distribution",
       x = "Species", y = "Count") +
  theme_minimal()

p1 + p2 +
  plot_annotation(
    title = "Study Population Demographics",
    theme = theme_minimal()
  )
```

\[Overview of the research problem and its significance\]

## Research Context

### Current State of Knowledge

\[Discussion of existing literature and knowledge gaps\]

```{r context-table, echo=FALSE}
# Create summary table of key characteristics
penguins %>%
  group_by(species) %>%
  summarise(
    Population = n(),
    `Mean Body Mass (g)` = mean(body_mass_g, na.rm = TRUE),
    `Mean Bill Length (mm)` = mean(bill_length_mm, na.rm = TRUE),
    `Mean Flipper Length (mm)` = mean(flipper_length_mm, na.rm = TRUE)
  ) %>%
  kable(caption = "Summary of Key Species Characteristics",
        digits = 1)
```

### Theoretical Framework

\[Description of theoretical framework guiding the research\]

@democrac2015

## Research Questions and Objectives

### Primary Research Questions

1.  \[First research question\]
2.  \[Second research question\]
3.  \[Third research question\]

### Research Objectives

\[Specific objectives of the dissertation\]

## Methodology Overview

```{r methodology-viz, fig.cap="Key Variable Relationships", echo=FALSE, warning=FALSE}
# Create correlation plot
penguins %>%
  select(bill_length_mm, bill_depth_mm, 
         flipper_length_mm, body_mass_g) %>%
  cor(use = "complete.obs") %>%
  as.data.frame() %>%
  rownames_to_column("Variable1") %>%
  pivot_longer(-Variable1, names_to = "Variable2", values_to = "Correlation") %>%
  ggplot(aes(Variable1, Variable2, fill = Correlation)) +
  geom_tile() +
  geom_text(aes(label = round(Correlation, 2)), color = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                      midpoint = 0, limit = c(-1,1)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Correlation Matrix of Key Measurements")
```

### Paper 1 Approach

\[Brief overview of Paper 1 methodology\]

### Paper 2 Approach

\[Brief overview of Paper 2 methodology\]

### Paper 3 Approach

\[Brief overview of Paper 3 methodology\]

## Geographic and Temporal Scope

```{r scope-viz, fig.cap="Geographic Distribution of Study Population", echo=FALSE}
ggplot(penguins, aes(x = island)) +
  geom_bar(aes(fill = species)) +
  facet_wrap(~year) +
  labs(title = "Population Distribution by Location and Year",
       x = "Island", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

\[Discussion of study scope and limitations\]

## Dissertation Structure

### Chapter Overview

\[Brief description of each chapter\]

```{r chapter-summary, echo=FALSE}
tribble(
  ~Chapter, ~Focus, ~Key_Methods, ~Data_Source,
  "Paper 1", "Species Distribution", "Descriptive Statistics", "Palmer Station",
  "Paper 2", "Morphological Analysis", "Comparative Analysis", "Palmer Station",
  "Paper 3", "Population Dynamics", "Time Series Analysis", "Palmer Station"
) %>%
  kable(caption = "Overview of Dissertation Chapters",
        col.names = c("Chapter", "Focus", "Key Methods", "Data Source"))
```

## Significance and Contribution

\[Expected contributions to theory and practice\]

## References
