
# Paper 2

## Abstract

\[Brief summary of the research, findings, and implications\]

## Introduction

### Background

\[Background of the research problem and context\]

```{r setup, include=FALSE}
library(palmerpenguins)
library(tidyverse)
library(knitr)
library(corrplot)
```

```{r}
#| label: fig-intro
#| fig-cap: "Penguin Body Mass Distribution by Species"
#| echo: false
ggplot(penguins, aes(x = species, y = body_mass_g, fill = species)) +
  geom_violin() +
  geom_boxplot(width = 0.2, alpha = 0.5) +
  labs(x = "Species", y = "Body Mass (g)", 
       title = "Body Mass Distribution by Penguin Species") +
  theme_minimal() +
  theme(legend.position = "none")
```

### Literature Review

\[Review of relevant literature and theoretical framework\]

@cheibub2010

### Research Questions

1.  Primary research question
2.  Secondary research questions

## Methods

### Data

\[Description of data sources and collection methods\]

```{r}
#| label: fig-correlation
#| fig-cap: "Correlation Matrix of Penguin Measurements"
#| echo: false
penguins %>%
  select(bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g) %>%
  cor(use = "complete.obs") %>%
  corrplot(method = "color", type = "upper", 
           tl.col = "black", tl.srt = 45)
```

```{r}
#| label: tbl-summary
#| tbl-cap: "Summary Statistics by Species and Sex"
#| echo: false
penguins %>%
  group_by(species, sex) %>%
  summarise(
    count = n(),
    mean_mass = mean(body_mass_g, na.rm = TRUE),
    sd_mass = sd(body_mass_g, na.rm = TRUE)
  ) %>%
  kable(caption = "Summary Statistics by Species and Sex",
        col.names = c("Species", "Sex", "Count", 
                     "Mean Mass (g)", "SD Mass (g)"),
        digits = 2)
```

### Analysis

\[Description of analytical approach and methods\]

```{r}
#| label: fig-results
#| fig-cap: "Flipper Length vs Body Mass by Species"
#| echo: false
ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_wrap(~sex) +
  labs(x = "Flipper Length (mm)", y = "Body Mass (g)") +
  theme_minimal()
```

## Results

### Primary Findings

\[Main results with supporting evidence\]

### Secondary Findings

\[Additional findings and analyses\]

## Discussion

### Theoretical Implications

\[How findings contribute to theory\]

### Practical Implications

\[Real-world applications and implications\]

### Limitations

\[Study limitations and constraints\]

## Conclusion

\[Summary of key findings and future research directions\]

## References
