# Paper 3

## Abstract

\[Brief summary of the research, findings, and implications\]

## Introduction

### Background

\[Background of the research problem and context\]

```{r setup, include=FALSE}
library(palmerpenguins)
library(tidyverse)
library(knitr)
library(patchwork)
```

```{r intro-plot, fig.cap="Penguin Measurements Across Islands", echo=FALSE}
#| label: fig-intro-plot
p1 <- ggplot(penguins, aes(x = island, y = bill_length_mm, fill = species)) +
  geom_boxplot() +
  labs(title = "Bill Length by Island", x = "", y = "Bill Length (mm)") +
  theme_minimal() +
  theme(legend.position = "none")

p2 <- ggplot(penguins, aes(x = island, y = flipper_length_mm, fill = species)) +
  geom_boxplot() +
  labs(title = "Flipper Length by Island", x = "", y = "Flipper Length (mm)") +
  theme_minimal()

p1 / p2
```

### Literature Review

\[Review of relevant literature and theoretical framework\]

@sitter2019

### Research Questions

1.  Primary research question
2.  Secondary research questions

## Methods

### Data

\[Description of data sources and collection methods\]

```{r island-summary, echo=FALSE}
#| label: tbl-island-summary
#| tbl-cap: "Population Distribution by Island and Species"
penguins %>%
  group_by(island, species) %>%
  summarise(
    total_count = n(),
    female_count = sum(sex == "female", na.rm = TRUE),
    male_count = sum(sex == "male", na.rm = TRUE),
    avg_body_mass = mean(body_mass_g, na.rm = TRUE)
  ) %>%
  kable(caption = "Population Distribution by Island and Species",
        col.names = c("Island", "Species", "Total Count", 
                     "Females", "Males", "Avg Mass (g)"),
        digits = 0)
```

### Analysis

\[Description of analytical approach and methods\]

```{r analysis-plots, fig.cap="Multi-dimensional Analysis of Penguin Characteristics", echo=FALSE, warning=FALSE}
#| label: fig-analysis-plots
p3 <- ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm)) +
  geom_point(aes(color = species, size = body_mass_g)) +
  facet_wrap(~island) +
  labs(x = "Bill Length (mm)", y = "Bill Depth (mm)") +
  theme_minimal()

p4 <- ggplot(penguins, aes(x = species, fill = sex)) +
  geom_bar(position = "dodge") +
  facet_wrap(~island) +
  labs(x = "", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p3 / p4
```

## Results

### Primary Findings

\[Main results with supporting evidence\]

### Secondary Findings

\[Additional findings and analyses\]

## Discussion

### Theoretical Implications

\[How findings contribute to theory\]

### Practical Implications

\[Real-world applications and implications\]

### Limitations

\[Study limitations and constraints\]

## Conclusion

\[Summary of key findings and future research directions\]

## References
